Deep Reinforcement Learning for Conservation Decisions

### 2021-09-29 manuscript/manuscript.Rmd
Added a WIP paragraph on behavioral ecology

>>>>

This paper does not set the precedent as the first application of RL to ecology.
In particular, there have been a number of studies applying RL to behavioral ecology, typically with multi-agent environments [@wang_reinforcement_2020, @frankenhuis_enriching_2019, @perolat_multi-agent_2017].
Yet, it is important to distinguish the aim of these behavioral studies from the aim of applying RL to conservation management.
In behavioral ecology RL studies, the authors employ RL agents to represent organisms.
Assuming that animals try to behave optimally under some objective, these authors then draw conclusions about animal behavior and evolution by observing how the RL agents learn.
When applying deep RL to conservation management, we do not make a similar logical leap to assuming that animals behave like RL agents.
We instead propose using RL as a way to search for solutions to unsolved decision-making problems in conservation.
